---
title: "Simple document"
date: 09-10-2024
author: Claudia Huynh
output: 
  html_document:
   toc: true
   toc_float: true
   code_floating: hide
---
```{r library_chunk, echo = FALSE, message = FALSE}
library (tidyverse)
```
I'm an R Markdown document! 
I loaded necessary packages from the library tidyverse

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r section_1_chunk, echo = FALSE}
# echo = wil give results but not the code
# eval. = FALSE will show the code but nothing will run in the background. Use it when you know for a fact the code doesn't work. 
# include = FALSE: code not displayed nor executed 
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.


# Learning Assessment

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r learning_assessment, message = FALSE}
la_df = 
  tibble(
  norm_samp = rnorm(500, mean = 1),
  norm_samp_logical = norm_samp > 0,
  norm_samp_abs = abs(norm_samp)
  )

ggplot (la_df, aes(x = norm_samp_abs)) + geom_histogram()
```